Leveraging Altruistic Peers to Reduce the Bandwidth Costs of Free Content Downloads

### 2008-06-24 docs/abstract/abstract.tex
Updated the abstract to the ACM class.

\documentclass[conference]{IEEEtran}

\usepackage[noadjust]{cite}

\usepackage[dvips]{graphicx}

\usepackage{url}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{threeparttable}
\usepackage{multirow}

@@

\title{Leveraging Altruistic Peers to Reduce the Bandwidth Costs of Free Content Downloads}
\author{\IEEEauthorblockN{Cameron Dale}
\IEEEauthorblockA{School of Computing Science (student)\\
Simon Fraser University\\
Burnaby, British Columbia, Canada\\
Email: camerond@cs.sfu.ca}
\and
\IEEEauthorblockN{Jiangchuan Liu}
\IEEEauthorblockA{School of Computing Science (faculty)\\
Simon Fraser University\\
Burnaby, British Columbia, Canada\\
Email: jcliu@cs.sfu.ca}}

@@

@@

We present a new peer-to-peer distribution model to meet these
demands. It is based on the lessons learned from many previous
implementations of successful peer-to-peer protocols, such as
Distributed Hash Tables and BitTorrent.
The model relies on the pre-existence of cryptographic
hashes of the content, which uniquely identify it for a request from
other peers. If the peer-to-peer download fails, then the original
request to the server is used as a fallback to prevent dissatisfied
users. The peer can then share this new content with others through
the P2P system. This system would efficiently satisfy the demands of
a large number of users, and should significantly reduce the
currently substantial bandwidth costs of hosting this content.

@@

Most Linux distributions use a software package management system
that fetches packages to be installed from a network of mirrors.
Debian-based distributions uses the \texttt{apt} program, which
downloads Debian packages from one of many mirrors. RPM-based
distributions use \texttt{yum}, and Gentoo uses \texttt{portage},
which both operate in a similar way. Other free software
distributors also use a similar system: CPAN distributes files
containing software packages for the PERL programming language,
using SOAP RPC requests to find and download files; Cygwin provides
many of the standard Unix/Linux tools in a Windows environment,
using a package management tool that requests packages from
websites; two software distribution systems exist for Mac OSX,
fink and MacPorts, that also retrieve packages in this way. Also,
some systems use direct web downloads, but with a hash verification
file also available for download next to the desired file. These
hash files usually have the same file name, but with an added
extension identifying the hash used (e.g. \texttt{.md5} for the MD5
hash). Finally, there are other programs that make use of
cryptographic hashing to identify files: e.g. Git is a version
control system in which all files and changes are identified by
their SHA1 hash.

@@

This situation presents a clear opportunity to use a new
peer-to-peer file sharing protocol.
A downloading peer can lookup the package hash using the protocol and, if it
is found, download the file from those peers and verify the content.
If the package hash can not be found, the peer will
fallback to downloading from the original content location, and once
complete will announce to other peers indicating that it now has
the content. The original servers or mirrors thus act as \emph{seeds} for the
P2P system without any modification to them.

This functionality could be directly integrated into the
package management software, although this would be
difficult as the protocol should be running at all times, whereas the
package software typically only runs until the download request is complete.
Alternatively, since many of the package management software
implementations use HTTP requests to download the files, it
it possible to implement the P2P aspect as as HTTP caching
proxy. The proxy will get uncached requests first from the P2P system,
and then fallback to the normal HTTP request from a server. For
methods that don't use HTTP requests, other types of proxies
(possibly custom-made) may also be possible.

@@

To demonstrate the ease and effectiveness of this solution we have
created a sample implementation called \texttt{apt-p2p} which
interacts with the \texttt{apt} tool found in most Debian-based
Linux distributions. \texttt{apt} uses SHA1 hashes to verify most
downloaded files, including the large index files that contain
information such as the hashes of the individual packages. Since all
requests from \texttt{apt} are in the form of HTTP downloads from a
server, the implementation takes the form of a caching HTTP proxy.

The DHT used is based on Khashmir, which is an implementation of
Kademlia \cite{kademlia} used by most of the existing BitTorrent
clients to implement trackerless operation. It has been modified to
better support the retrieval of multiple values (peers) per key, and to
improve the response time so as to satisfy users' demands for speed.
The values stored in the DHT are all bencoded dictionaries similar
to torrent files. Peers store their download location (IP address
and TCP port), as well as the piece strings (or hashes of piece
strings) as described in the previous section. Downloading is
accomplished by simple HTTP requests for the hash of the file,
which is sent to the peers identified from the DHT lookup to
have the desired file. All peers support HTTP/1.1, both as
servers and clients, which allows for pipelining of multiple
requests to a peer, and the requesting of smaller pieces of a large
file using the Range request header.

@@

\bibliographystyle{IEEEtran}
\bibliography{./IEEEabrv,./all}

>>>>

\documentclass{sig-alt-release2}

\usepackage[noadjust]{cite}
\usepackage{url}
\hyphenation{dis-tri-bu-ted}

@@

\conferenceinfo{SIGCOMM'08,} {August 17--22, 2008, Seattle, Washington, USA.} 
\CopyrightYear{2008}
\crdata{978-1-60558-175-0/08/08}

\title{Leveraging Altruistic Peers to Reduce the Bandwidth Costs of Free Content Downloads}
\numberofauthors{2}
\author{
\alignauthor Cameron Dale\\
	\affaddr{School of Computing Science (student)}\\
	\affaddr{Simon Fraser University}\\
	\affaddr{Burnaby, British Columbia, Canada}\\
	\email{Email: camerond@cs.sfu.ca}
%\and
\alignauthor Jiangchuan Liu\\
	\affaddr{School of Computing Science (faculty)}\\
	\affaddr{Simon Fraser University}\\
	\affaddr{Burnaby, British Columbia, Canada}\\
	\email{Email: jcliu@cs.sfu.ca}
}

@@

\begin{abstract}
We introduce the opportunity many free content distributors have to
reduce their bandwidth costs using a peer-to-peer download
mechanism. Our model for this peer-to-peer distribution is simple to
implement, backwards-compatible with the existing infrastructure,
and can be deployed incrementally. It makes wide use of a customized
distributed hash table (DHT) to facilitate the finding of peers and
the efficient downloading of files. We also present the example
solution we created for one of these distributors, the Debian
project, which is already in use by some users.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{C.2.4}{Computer-Communication Networks}{Distributed Systems}[Distributed applications]
\terms{Design, Performance, Reliability}
\keywords{BitTorrent, P2P}

@@

We present a new peer-to-peer distribution model to meet these
demands, based on other successful peer-to-peer protocols such as
Distributed Hash Tables and BitTorrent.
The model relies on the pre-existence of cryptographic
hashes of the content, which uniquely identify it for a request from
other peers. If the peer-to-peer download fails, then the original
request to the server is used as a fallback to prevent dissatisfied
users. The peer can then share this new content with others through
the P2P system. This system would efficiently satisfy the demands of
a large number of users, and should significantly reduce the
currently substantial bandwidth costs of hosting this content.

@@

Most Linux distributions use a software package management system
that fetches packages to be installed from a network of mirrors.
Debian-based distributions uses the \texttt{apt} program, which
downloads Debian packages from one of many mirrors. RPM-based
distributions use \texttt{yum}, and Gentoo uses \texttt{portage},
which both operate in a similar way. Other free software
distributors also use a similar system: CPAN distributes files
containing software packages for the PERL programming language,
using SOAP RPC requests to find and download files; Cygwin provides
many of the standard Unix/Linux tools in a Windows environment,
using a package management tool that requests \texttt{tar} files from
websites; two software distribution systems exist for Mac OSX,
fink and MacPorts, that also retrieve packages in this way. Also,
some systems use direct web downloads, but with a hash verification
file also available. These
hash files usually have the same file name, but with an added
extension identifying the hash used (e.g. \texttt{.md5} for the MD5
hash). Finally, there are other programs that make use of
cryptographic hashing to identify files: e.g. Git is a version
control system in which all files and changes are identified by
their SHA1 hash.

@@

This situation presents a clear opportunity to use a new
peer-to-peer file sharing protocol.
A downloading peer can lookup the package hash using the protocol and, if it
is found, download the file from those peers and verify the content.
If the package hash can not be found, the peer will
fallback to downloading from the original content location, and once
complete will announce to other peers indicating that it now has
the content. The original servers or mirrors thus act as \emph{seeds} for the
P2P system without any modification to them, and users are satisfied even when
there are no peers which allows the system to be deployed incrementally.

This functionality could be directly integrated into the
package management software, although this would be
difficult as the protocol should be running at all times, whereas the
package software typically only runs until the download request is complete.
Alternatively, it
it possible to implement the P2P aspect as a caching
proxy. The proxy will get uncached requests first from the P2P system,
and then fallback to the normal request from a server.

@@

To demonstrate the ease and effectiveness of this solution we have
created a sample implementation called \texttt{apt-p2p} which
interacts with the \texttt{apt} tool found in most Debian-based
Linux distributions. \texttt{apt} uses SHA1 hashes to verify most
downloaded files, including the large index files that contains detailed
information such as the hashes of the individual packages. Since all
requests from \texttt{apt} are in the form of HTTP downloads from a
server, the implementation takes the form of a caching HTTP proxy.

The DHT used is based on Khashmir, which is an implementation of
Kademlia \cite{kademlia} used by most of the existing BitTorrent
clients to implement trackerless operation. It has been modified to
better support the retrieval of multiple values (peers) per key, and to
improve the response time so as to satisfy users' demands for speed.
The values stored in the DHT are all bencoded dictionaries similar
to torrent files. Peers store their download location (IP address
and TCP port), as well as the piece strings (or hashes of piece
strings) as described in the previous section. Downloading is
accomplished by simple HTTP requests for the hash of the file,
which is sent to the peers identified in a DHT lookup to
have the desired file. All peers support HTTP/1.1, both as
servers and clients, which allows for pipelining of multiple
requests to a peer, and the requesting of smaller pieces of a large
file using the Range request header.

@@

\bibliographystyle{abbrv}
\bibliography{./all}
